\section{Introduction}
\subsection{System overview}
\par WeCalEvent is a platform where users are able to create and manage their events and invite other
users. Information about time and place of the event should be provided while creation of the event.
\par The system alerts the event creator 3 days before the event day in case of weather condition alteration
and suggests him the closest day with suitable weather.
Invited users will be able to decline or accept the invitation. All event participants will be notified
in case of weather forecast alteration a day before the event.
\par This platform is sufficient for users who look forward to schedule their events according to the
weather conditions.
\subsection{Purpose of this document}
\par The purpose of this acceptance test is to make sure that the project complies with the requirements of requirement documents.
\subsection{Intended audience}
\par The intended audience is:
\begin{itemize}
  \item Team members
  \item Course staff
\end{itemize}

\subsection{Scope} This document includes the plan, items, scope, approach, environment and procedure of WeCalEvent
acceptance test. After that, the responsibilities of developers and user representatives are identified. At
last, risks and contingencies are specified to ensure the test reliability. Other information not related to the
test activities is not included in this document.
\subsection{Definitions}
\begin{tabular}{|l|l|}
  \hline
  % after \\: \hline or \cline{col1-col2} \cline{col3-col4} ...
  \textbf{Keyword} & \textbf{Definition} \\
  \hline
  User & Is someone, who uses the application. \\
  \hline
  System & Our application \\
  \hline
\end{tabular}
