\newpage

\begin{center}
\section{Conceptual model for software design descriptions}
\end{center}

\subsection{Software design in context}
\par In MeteoCal project, object oriented approach will be used as a design method. Hence, it will be easier to implement the project and add possible future features. Since this project is a social network application, this property is critically important. Furthermore multi-layered system architecture will be used. Database, business and client layers will help modularity and adaptability of the software. With object oriented design and multi-layered architecture, portability and integrability between components will be improved.

\subsection{Software design descriptions within the life cycle}
\subsubsection{Influences on DD preparation}
\par The key software life cycle product that drives a software design is typically the requirements analysis and specification (RASD) document. RASD captures the software requirements (product perspective, functional and non-functional requirements and interface requirements) that will drive the design and design constraints to be considered or observed.
\subsubsection{Influences on software life cycle products}
\par The software Design document influences the content of several major software life cycle work products. During the preparation of DD and during the implementation stage of the project requirements may change. Hence DD influences will lead to requirements changes. Besides, DD will influence test plans and test documentation of the MeteoCal project.
\subsubsection{Design verification and design role in validation}
\par Test cases will be prepared after the development phase. Verification of the software will be tested with these test cases and all parts will be evaluated. Success of the software system will be determined with test cases. After the test results, validation of the software will be checked if requirements of the system are fulfilled or not.
